```{r, echo=FALSE, include=FALSE}
## Get VERSION and create file names
ver <- sub(x=grep(x=readLines("DESCRIPTION"), pattern="^Version: ",
                  value=TRUE),
           pattern="^Version: ", replacement="")
pkg.name <- "mcglm_"
pkg.source <- paste0(pkg.name, ver, ".tar.gz")
pkg.win <- paste0(pkg.name, ver, ".zip")
```

# mcglm `r ver`

The `mcglm` package fits multivariate covariance generalized linear models
(Bonat and Jorgensen, 2016).

## Introduction

`mcglm` is an R package designed to fit Multivariate Covariance Generalized Linear Models.
It allows you to specify a distinct linear predictor for each response variable, 
offering exceptional flexibility for analyses involving multiple outcomes.

With `mcglm`, you can model a wide range of response types — continuous, discrete 
(such as counts and binary), limited, and even zero inflated responses, 
whether continuous or mixed.

Its main strength lies in the ability to capture complex relationships among 
variables through multiple covariance structures, enabling more realistic and 
robust multivariate modeling.

This package was developed as part of the Wagner's Ph.D. thesis, 
combining academic rigor with practical value for the statistical modeling community.

## Download and install

### Linux/Mac

Use the `devtools` package (available from
[CRAN](http://cran-r.c3sl.ufpr.br/web/packages/devtools/index.html)) to
install automatically from this GitHub repository:

```{r, eval=FALSE}
library(devtools)
install_github("bonatwagner/mcglm")
```

Alternatively, download the package tarball: [`r pkg.source`][]
and run from a UNIX terminal (make sure you are on the container file
directory):

```{r, echo=FALSE, comment=NA}
cmd <- paste("R CMD INSTALL -l /path/to/your/R/library", pkg.source)
cat(cmd, sep = "\n")
```

Or, inside an `R` session:

```{r, echo=FALSE, comment=NA}
inst <- paste0("install.packages(", "\"", pkg.source, "\"", ", repos = NULL,\n",
               "                 lib.loc = \"/path/to/your/R/library\",\n",
               "                 dependencies = TRUE)")
cat(inst, sep = "\n")
```

Note that `-l /path/to/your/R/library` in the former and `lib.loc =
"/path/to/your/R/library"` in the latter are optional. Only use it if
you want to install in a personal library, other than the standard R
library.

### Windows

Download Windows binary version: [`r pkg.win`][] (**do not unzip
it under Windows**), put the file in your working directory, and from
inside `R`:

```{r, echo=FALSE, comment=NA}
instw <- paste0("install.packages(", "\"", pkg.win, "\"", ", repos = NULL,\n",
                "                 dependencies = TRUE)")
cat(instw, sep = "\n")
```

## Authors

- [Wagner Hugo Bonat][] (author and main developer)

## Documentation

The reference manual in PDF can be found here: [mcglm-manual.pdf][]

## Contributing

This R package is develop using [`roxygen2`][] for documentation and
[`devtools`] to check and build. Also, we adopt the [Gitflow worflow][]
in this repository. Please, see the
[instructions for contributing](./CONTRIBUTING.md) to collaborate.

## License

This package is released under the
[GNU General Public License (GPL) v3.0][].

See [LICENSE](./LICENSE)

<!-- links -->

[GNU General Public License (GPL) v3.0]: https://www.gnu.org/licenses/gpl-3.0.html
[`roxygen2`]: https://github.com/klutometis/roxygen
[`devtools`]: https://github.com/hadley/devtools
[`r pkg.source`]: https://github.com/bonatwagner/mcglm/blob/main/mcglm_0.9.0.tar.gz
[mcglm-manual.pdf]: https://github.com/bonatwagner/mcglm/blob/main/mcglm.Rcheck/mcglm-manual.pdf
[Gitflow worflow]: https://nvie.com/posts/a-successful-git-branching-model/
[Wagner Hugo Bonat]: https://www.linkedin.com/in/wagner-bonat
